### 2020-04-26 README.Rmd
Add worcs badge

---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->
<!--[![CRAN status](https://www.r-pkg.org/badges/version/worcs)](https://cran.r-project.org/package=worcs)
[![](https://cranlogs.r-pkg.org/badges/worcs)](https://cran.r-project.org/package=worcs)-->
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/cjvanlissa/worcs.svg?branch=master)](https://travis-ci.org/cjvanlissa/worcs)
<!--[![Codecov test
coverage](https://codecov.io/gh/cjvanlissa/worcs/branch/master/graph/badge.svg)](https://codecov.io/gh/cjvanlissa/worcs?branch=master)-->
<!--[![DOI](http://joss.theoj.org/papers/10.21105/joss.00978/status.svg)](https://doi.org/10.21105/joss.00978)-->
# WORCS

@@

>>>>

---
output: github_document
---

# WORCS <a href='https://osf.io/zcvbs/'><img src='paper/worcs_icon.png' align="right" height="139" /></a>

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!--[![CRAN status](https://www.r-pkg.org/badges/version/worcs)](https://cran.r-project.org/package=worcs)
[![](https://cranlogs.r-pkg.org/badges/worcs)](https://cran.r-project.org/package=worcs)-->
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/cjvanlissa/worcs.svg?branch=master)](https://travis-ci.org/cjvanlissa/worcs)
<!--[![Codecov test
coverage](https://codecov.io/gh/cjvanlissa/worcs/branch/master/graph/badge.svg)](https://codecov.io/gh/cjvanlissa/worcs?branch=master)-->
<!--[![DOI](http://joss.theoj.org/papers/10.21105/joss.00978/status.svg)](https://doi.org/10.21105/joss.00978)-->
# WORCS

@@

## Acknowledgements

The worcs logo makes use of the gear, services, gears, preferences, settings icon, made by MD Badsha Meah from www.freeicons.io.
